\documentclass{screenplay}[2012/06/30]

\title{That time we went to trivia}
\author{Clement Fung}

\begin{document}
\coverpage

\fadein
\intslug[day]{The NSS Lab}

A smoky and slow afternoon. Everyone is a bit antsy, weighed down by the day's work.

\begin{dialogue}{Stewart} God damn it Vaastav, you've done it again. \end{dialogue}
\begin{dialogue}{Vaastav} How so? \end{dialogue}

The sounds of typing in the lab stop. An awkward silence.

\begin{dialogue}{Stewart}[louder] How many times do I need to tell you this man? Spaces, not tabs! It's the second time today! \end{dialogue}

Everyone is taken aback. Uncharacteristic. Stew pauses, surprised with himself. 

\begin{dialogue}{Amy}[nervous] ...are you okay Stew? \end{dialogue}
\begin{dialogue}{Vaastav} Stew, we both know its not about that. You're not yourself these days. \end{dialogue}

They are right and STEWART knows it.

\begin{dialogue}{Stewart} For 2 years I've been fighting invariants. Every single day. Now that I've finished my thesis, what's next? All I've done since is format this stupid Latex document. \end{dialogue}

\begin{dialogue}{Vaastav}[cutting in] Dude, you're done! You're free! We chanted for you! Why can't you just be happy!? \end{dialogue}

\begin{dialogue}{Amy} Yeah Stew, don't be so hard on yourself. You should be proud of what you've accomplished here. Pretty soon, you'll be off to San Diego, doing bigger and better things! \end{dialogue}

\begin{dialogue}{Stewart} Yeah I know, but seriously, is this all that's left for me to do here? Is Latex formatting and paperwork really how it ends for me? I swear, September can't come soon enough... \end{dialogue}

CLEMENT enters from the lab door.

\begin{dialogue}{Clement} Hey guys, it's 620! Trivia time. \end{dialogue}

Everyone looks at each other. Too easy. All this time, the solution was right there.

\begin{dialogue}{Stewart} You're on bud! \end{dialogue}

\fadeout
\theend

\end{document}